### 2020-05-27 README.Rmd
updated lifecycle to experimental, with warning on readme

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R build status](https://github.com/AIMS/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/AIMS/dataaimsr/actions)
![pkgdown](https://github.com/AIMS/dataaimsr/workflows/pkgdown/badge.svg)
[![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](https://choosealicense.com/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg)](commits/master)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/AIMS/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/AIMS/dataaimsr/actions)
![pkgdown](https://github.com/AIMS/dataaimsr/workflows/pkgdown/badge.svg)
[![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](https://choosealicense.com/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg)](commits/master)
<!-- badges: end -->

## Warning

**This package and its API dependency are a work in progress. So we advise not installing this package just yet as many of the functionalities may change or simply become deprecated.**
